---
title: "Formative Assessments"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(parsons)
library(tidyverse)
tutorial_options(exercise.eval = TRUE)
mtcars <- mtcars %>% 
  as_tibble() %>% 
  mutate_at(c("vs", "am", "cyl"), as.factor)
```


## Exercise 1

Drag the statements from the top panel to the bottom panel to produce the desired plot:

```{r ex1, echo=FALSE}
question_parsons(
  initial = c(
      "geom_point() +",
      "labs(title = \"A Scatterplot\") +",
      "geom_smooth(method = \"lm\") +",
      "mtcars %>%",
      "facet_grid(~ vs) +",
      "theme(legend.position = \"bottom\")",
      "ggplot(aes(x = hp, y = mpg, color = cyl)) +"
      ),
  answer(
    c(
      "mtcars %>%",
      "ggplot(aes(x = hp, y = mpg, color = cyl)) +",
      "geom_point() +",
      "geom_smooth(method = \"lm\") +",
      "facet_grid(~ vs) +",
      "labs(title = \"A Scatterplot\") +",
      "theme(legend.position = \"bottom\")"
      ),
    correct = TRUE
  ),
  problem_type = "base"
)
```

## Exercise 2

Plot a Bar Plot with the number of hears in the X-axis and the size of the bars as the Horsepower and color **inside** the bars as the number of cylinders (`cyl`). Facet the plot by type of engine (`vs`). Finally, add a title with the text `"Bar Plot"`.

```{r ex2, exercise=TRUE, exercise.lines = 7, exercise.eval = TRUE}
mtcars %>%
  ggplot(aes())
```

```{r ex2-solution}
mtcars %>% 
  ggplot(aes(x = gear, y = hp, fill = cyl)) +
  geom_col() +
  facet_wrap(~ vs) +
  labs(title = "Bar Plot")
```

<div id="ex2-hint">
**Hint:**
* Start with `ggplot(aes(x = gear, y = hp, fill = cyl))`
* then add `geom_col()`
* followed by a `facet_wrap()`
* finalize with a `labs(title = "Bar Plot")` 
</div>

```{r ex2-check}
"Good job!"
```
